---
title: "Deployment Example"
author: "ForwardKeys - Team 01"

output: 
  flexdashboard::flex_dashboard:
    theme: spacelab
    orientation: rows
    social: menu
    source_code: embed
runtime: shiny
---
<style type="text/css">

.chart-title {  /* chart_title  */
   font-size: 30px;
   font-family: Buffalo;

</style>

```{css}
.chart-wrapper .chart-stage {
    overflow-y: auto;
}
```


```{r global, include=FALSE}

library(arules)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(reshape2)
library(flexdashboard)
library(shiny)
library(shinyWidgets)
options(shiny.maxRequestSize = 600*1024^2)
datasett = reactiveValues()
data_attack = read.csv(file = 'Nov2015.csv', sep= ';')
data_compare = read.csv(file = 'Nov2014.csv', sep = ';')

data_attack = data_attack[data_attack$bookingdate %in% sort(unique(data_attack$bookingdate))[substring(sort(unique(data_attack$bookingdate)),6) %in% substring(sort(unique(data_compare$bookingdate)),6)], ]  
data_compare = data_compare[data_compare$bookingdate %in% sort(unique(data_compare$bookingdate))[substring(sort(unique(data_compare$bookingdate)),6) %in% substring(sort(unique(data_attack$bookingdate)),6)], ]  
```

# HELP
## row 1 {data-height=650}

### Explanation and Guidelines

This is the deployment of our model based on association rules, where we tried to find the attributes of the passengers that most influence a full cancellation due to a major disaster on the destination, however, it is generalized for any type of bookingsign (partial_cancellation, partial_addition and new_booking).

It is also ready to be used by **FordwardKeys**, to easily explore more events like this attack on Paris.\
**Note:** In this model data is already loaded as an example to show the potential of the application.

__HOW TO NAVIGATE THE APP__

<ol>
<li>On the DASHBOARD page, select the bookingsign to analyse and click compute rules (we can change it as many times as we want).
     The rules (attributes) will be plotted on the first chart by their score (influence on the event year).</li>
<li>Choose the combination of attributes to plot and press update, the second page of plots will show the relative frequency of the bookingsign selected for the datasets with and without the conditions, to easily compare them. As of right now it is not robust to errors, so if a combination of attributes does not exist in the data, the app will stop working.</li>
<li>A variety of metrics and information about the attack will be shown on the last tab. </li>

</ol>

```{r}
progressBar(id = "startpb", value = 100, display_pct = TRUE, size = 'lg')
```

## row 2 {data-width=350, .tapset}

### CSV with event data 
```{r}
fileInput("file1", "File is ready. Do not enter data",
        accept = c(
          "text/csv",
          "text/comma-separated-values,text/plain",
          ".csv"))
```

### CSV with comparison data 
```{r}
fileInput("file2", "File is ready. Do not enter data",
        accept = c(
          "text/csv",
          "text/comma-separated-values,text/plain",
          ".csv"))
```


# DASHBOARD

## Column {.sidebar}


```{r}
selectInput(inputId = "bookingsign",
                  label = "Type of transaction:",
                  choices = unique(data_attack$bookingsign), selected = 'FULL_CANCELLATION',
                  multiple = F
                  )
actionBttn("reload", "COMPUTE RULES", color = 'warning', style = 'simple', size = 'sm')
progressBar(id = "reloadpb", value = 0, display_pct = TRUE)

selectInput(inputId = "mode",
                  label = "Choose pax attributes:",
                  choices = NULL,
                  multiple = T
                  )

actionBttn("update", "UPDATE", color = 'success', style = 'simple', size = 'sm')
dateInput("dateattack", label = "Doom Day", value = "2015-11-13")
numericInput("attackuntil", label ="Temporal extent of the attack (days)", value = 10)
```


```{r}

observeEvent(input$reload,{
  req(input$bookingsign)
  
updateProgressBar(session = session, id = "reloadpb", value = 10)
rules_attack_df = data_attack[, c("bookingsign","paxprofile","losname","cabinclass","distchannel")]
updateProgressBar(session = session, id = "reloadpb", value = 15)
rules_compare_df = data_compare[, c("bookingsign","paxprofile","losname","cabinclass","distchannel")]
updateProgressBar(session = session, id = "reloadpb", value = 25)
rules_attack_df = as(rules_attack_df, "transactions")
updateProgressBar(session = session, id = "reloadpb", value = 35)
rules_compare_df = as(rules_compare_df, "transactions")
updateProgressBar(session = session, id = "reloadpb", value = 50)

rules_attack <- apriori (data=rules_attack_df, parameter=list (supp=0.001, conf = table(data_attack$bookingsign)[[input$bookingsign]]/sum(table(data_attack$bookingsign))), appearance = list(default="lhs",rhs=paste("bookingsign=", input$bookingsign, sep = '')), control = list (verbose=F))
updateProgressBar(session = session, id = "reloadpb", value = 70)
rules_compare <- apriori (data=rules_compare_df, parameter=list (supp=0.001, conf = table(data_attack$bookingsign)[[input$bookingsign]]/sum(table(data_attack$bookingsign))), appearance = list(default="lhs",rhs=paste("bookingsign=", input$bookingsign, sep = '')), control = list (verbose=F))
updateProgressBar(session = session, id = "reloadpb", value = 80)

datalist = list()
n = 0
for (i in colnames(rules_attack_df)){
  skip = F
  tryCatch(
    expr = {
      n = n + 1
      sub = DATAFRAME(subset(rules_attack, subset = lhs %in% i))
      sub2 = DATAFRAME(subset(rules_compare, subset = lhs %in% i))
      dat = data.frame(condition = i, value = sum(log(sub$support) * sub$confidence * sub$lift^2) / sum(log(sub2$support) * sub2$lift^2 * sub2$confidence), quantity_attack = max(sub$count), quantity_compare = max(sub2$count))
      datalist[[n]] = dat },
    error = function(e) {skip = T}
  )
  if(skip) {next}

}
updateProgressBar(session = session, id = "reloadpb", value = 90)
datasett$mainRules = do.call(rbind, datalist)

datasett$mainRules = datasett$mainRules[order(datasett$mainRules$value, decreasing = T),]
updateProgressBar(session = session, id = "reloadpb", value = 100)
# vtop = c()
# vmin = c()
# 
# for (s in c(1,2)) {
# vtop = c(vtop, str_split(top_n(mainRules, 2, value)$condition[s], "="))
# vmin = c(vmin,str_split(top_n(mainRules,- 2, value)$condition[s], "="))
# str_split(mainRules$condition[1], '=')
# }

updateSelectInput(inputId = "mode",choices = datasett$mainRules$condition, selected = datasett$mainRules$condition[1])
 
                  
})             
                
```



```{r}
observeEvent(input$update, {
  req(input$mode)
  

fix1 = data_attack[, c("bookingdate", "bookingsign","paxprofile","losname","cabinclass","distchannel")]
fix2 = data_compare[, c("bookingdate", "bookingsign","paxprofile","losname","cabinclass","distchannel")]
datasett$attackmetrics$day = match(strftime(input$dateattack, "%Y-%m-%d") , sort(unique(data_attack$bookingdate)))



g1 = fix1 %>% count(bookingsign, bookingdate)
g1 = g1[g1$bookingsign == input$bookingsign,]
g1$values = g1$n/(fix1 %>% count(bookingdate))$n
datasett$attackmetrics$g1cond = g1$n
datasett$attackmetrics$g1 = (fix1 %>% count(bookingdate))$n

g2 = fix2 %>% count(bookingsign, bookingdate)
g2 = g2[g2$bookingsign == input$bookingsign,]
g2$values = g2$n/(fix2 %>% count(bookingdate))$n
datasett$attackmetrics$g2cond = g2$n
datasett$attackmetrics$g2 = (fix2 %>% count(bookingdate))$n

for (i in 1:length(input$mode)) {
  var_condition = unlist(str_split(input$mode[i], '='))
  fix1 = fix1[fix1[[var_condition[1]]] == var_condition[2],]
  fix2 = fix2[fix2[[var_condition[1]]] == var_condition[2],]
}


counts1 = fix1 %>% count(bookingsign, bookingdate)
counts1 = counts1[counts1$bookingsign == input$bookingsign,]
counts1$partial = counts1$n/(fix1 %>% count(bookingdate))$n
datasett$attackmetrics$c1cond = counts1$n
datasett$attackmetrics$c1 = (fix1 %>% count(bookingdate))$n
 
counts2 = fix2 %>% count(bookingsign, bookingdate)
counts2 = counts2[counts2$bookingsign == input$bookingsign,]
counts2$partial = counts2$n/(fix2 %>% count(bookingdate))$n
datasett$attackmetrics$c2cond = counts2$n
datasett$attackmetrics$c2 = (fix2 %>% count(bookingdate))$n

datasett$forplot = data.frame(partial_attack = counts1$partial, partial_compare = counts2$partial, total_attack = g1$values, total_compare = g2$values)
datasett$forplot = melt(datasett$forplot, variable.name = 'year')

year_attack = unlist(str_split(data_attack$bookingdate[1], "-"))[1]
year_compare = unlist(str_split(data_compare$bookingdate[1], "-"))[1]
days = length(unique(data_attack$bookingdate))
datasett$forplot$Year = c(rep(year_attack, days), rep(year_compare, days), rep(year_attack, days), rep(year_compare, days))

msg = "Only passengers with\n"
for (val in input$mode) {
  msg = paste(msg, paste(val, collapse = '=', sep=''), ' & ', sep ='')
}

datasett$forplot$Applied_to = c(rep(gsub('.{3}$', '', msg), days*2),
                         rep('All passengers', days*2))

})
```

## Column {.tabset .tabset-fade}

### Best attributes plot

```{r}
renderPlot({
  req(datasett$mainRules)
  
  
  ggplot(datasett$mainRules, aes(x = reorder(datasett$mainRules$condition, -datasett$mainRules$value), y=datasett$mainRules$value, fill = datasett$mainRules$value > 1)) +
    geom_bar(stat="identity") + scale_fill_manual('Influential for event year', values = c("firebrick", "lightgreen"), labels = c(paste('Contributes to avoid a', input$bookingsign), paste('Contributes to a', input$bookingsign))) + 
    geom_hline(yintercept=1, linetype="dashed", color = "red") +     
    labs(title= paste("Most important attributes for a", input$bookingsign,"transaction on the event year"),
        y ="Score\n", x = "Attributes") +
    theme_bw() +
      theme(axis.text.x = element_text(angle = 90), plot.title = element_text(hjust = 0.5)) 
  
  
})
```

The higher the score, the more impactful that attribute of the passenger is for a `r reactive(input$bookingsign)` transaction. For full cancellations for example, attributes losname=STAY and paxprofile=BUSINESS have high scores, that means people with those attributes were more likely to cancel during the time of the attack, specially in comparison with a normal month. Knowing this information beforehand would enable us to get ready for "crystal" passengers, in case of a major disaster. 

On the other hand, the red bars mean that people with those characteristics were less likely to cancel during the attack (specially in comparison with a normal month). This information is crucial as it lets us know which kind of passengers would travel notwithstanding any problem in the destination. 

You can choose a combination of attributes in the left side of the DASHBOARD page, click the button, and the plot will update. Notice how big the difference is between the month of the event with the conditions and the other lines. Notice also how there is no big difference between the normal month and the normal month with the conditions, this is because the conditions of the passengers are specially important for a cancellation due to the event/attack, not for any other reason.

### Relative `r reactive(input$bookingsign)` plot

 

```{r}

renderPlot({
  req(datasett$forplot) 
  
  ggplot(datasett$forplot, aes(x = rep(1:(nrow(datasett$forplot)/4),4), y=datasett$forplot$value)) +
  geom_line(aes(color = datasett$forplot$Year, linetype = datasett$forplot$Applied_to), size = 1.2) +
  labs(title= paste(input$bookingsign,"throughout the month"),
        y =paste("% of transactions that are" ,input$bookingsign,"\n"), x = "Days", color = "Year", linetype = "Applied to") +
  theme_bw() +

  theme(plot.title = element_text(hjust = 0.5))
})
```

### Attack Metrics

**Day of the attack:** `r reactive(strftime(input$dateattack, "%Y-%m-%d"))`

**Information about the day of the attack**\
`r reactive(input$bookingsign)` on that day => `r reactive(datasett$attackmetrics$g1cond[datasett$attackmetrics$day])`\
`r reactive(input$bookingsign)` on that day by people with `r reactive(input$mode)` => `r reactive(datasett$attackmetrics$c1cond[datasett$attackmetrics$day])`\
Which accounts for `r reactive(round(datasett$attackmetrics$c1cond[datasett$attackmetrics$day]/datasett$attackmetrics$g1cond[datasett$attackmetrics$day],2) * 100)`% of the people

In comparison with last year's data...

`r reactive(input$bookingsign)` on that day, last year => `r reactive(datasett$attackmetrics$g2cond[datasett$attackmetrics$day])`\
`r reactive(input$bookingsign)` on that day by people with `r reactive(input$mode)`, last year => `r reactive(datasett$attackmetrics$c2cond[datasett$attackmetrics$day])`\
Which accounts for `r reactive(round(datasett$attackmetrics$c2cond[datasett$attackmetrics$day]/datasett$attackmetrics$g2cond[datasett$attackmetrics$day],2) * 100)`% of the people

There has been a change of `r reactive(round((datasett$attackmetrics$g1cond[datasett$attackmetrics$day] - datasett$attackmetrics$g2cond[datasett$attackmetrics$day])/ datasett$attackmetrics$g1cond[datasett$attackmetrics$day],2) * 100)`% from last year to the event year in `r reactive(input$bookingsign)`\
For the people with `r reactive(input$mode)`, there has been a change of `r reactive(round((datasett$attackmetrics$c1cond[datasett$attackmetrics$day] - datasett$attackmetrics$c2cond[datasett$attackmetrics$day])/datasett$attackmetrics$c2cond[datasett$attackmetrics$day],2) * 100)`% from last year to the event year in `r reactive(input$bookingsign)`

----------------------------------
**Information about the extent of the attack**\
`r reactive(input$bookingsign)` during that time => `r reactive(sum(datasett$attackmetrics$g1cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]))`\
`r reactive(input$bookingsign)` during that time by people with `r reactive(input$mode)` => `r reactive(sum(datasett$attackmetrics$c1cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]))`\
Which accounts for `r reactive(round(sum(datasett$attackmetrics$c1cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)])/sum(datasett$attackmetrics$g1cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]),2) * 100)`% of the people

In comparison with last year's data...

`r reactive(input$bookingsign)` during that time, last year => `r reactive(sum(datasett$attackmetrics$g2cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]))`\
`r reactive(input$bookingsign)` during that time by people with `r reactive(input$mode)`, last year => `r reactive(sum(datasett$attackmetrics$c2cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]))`\
Which accounts for `r reactive(round(sum(datasett$attackmetrics$c2cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)])/sum(datasett$attackmetrics$g2cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]),2) * 100)`% of the people

There has been a change of `r reactive(round((sum(datasett$attackmetrics$g1cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]) - sum(datasett$attackmetrics$g2cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]))/sum( datasett$attackmetrics$g1cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]),2) * 100)`% from last year to the event year in `r reactive(input$bookingsign)`\
For the people with `r reactive(input$mode)`, there has been a change of `r reactive(round((sum(datasett$attackmetrics$c1cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]) - sum(datasett$attackmetrics$c2cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]))/sum(datasett$attackmetrics$c2cond[datasett$attackmetrics$day: (datasett$attackmetrics$day + input$attackuntil)]),2) * 100)`% from last year to the event year in `r reactive(input$bookingsign)`


