---
title: "Intento1"
author: "El súper equipo de proyecto"

output: 
  flexdashboard::flex_dashboard:
    theme: spacelab
    orientation: rows
    social: menu
    source_code: embed
runtime: shiny
---
<style type="text/css">

.chart-title {  /* chart_title  */
   font-size: 30px;
   font-family: Buffalo;

</style>

```{r global, include=FALSE}

library(arules)
library(dplyr)
library(ggplot2)
library(tidyverse)
library(reshape2)
library(flexdashboard)
library(shiny)
library(shinyWidgets)
options(shiny.maxRequestSize = 600*1024^2)
datasett = reactiveValues()
```

```{r}
data_attack <- eventReactive(input$file1,{
      data_attack <- read.csv(input$file1$datapath, sep= ';')
       
    })
data_compare <- eventReactive(input$file2,{
      data_compare <- read.csv(input$file2$datapath, sep= ';')
    })
```

# HELP
## row 1 {data-height=650}

### Explanation and Guidelines

This is the deployment of our model based on association rules, where we tried to find the attributes of the passengers that most influence a full cancellation due to a major disaster on the destination, however, it is generalized for any type of bookingsign (partial_cancellation, partial_addition and new_booking).

It is also ready to be used by **FordwardKeys**, to easily explore more events like this attack on Paris.

__HOW TO NAVIGATE THE APP__

<ol>
<li>Select the datasets (csv, ; separated) to examine, top-right for the data of the event, bottom-right for the data to compare with. **Note**: Datasets need to share the same timeframe</li>

<li>Data will start to load (watch the progress bar update)</li>
<li>On the DASHBOARD page, select the bookingsign to analyse and click compute rules (we can change it as many times as we want)
     The rules (attributes) will be plotted on the first chart by their score (influence on the event year)</li>
<li>Choose the combination of attributes to plot and press update, the second page of plots will show the relative frequency of the bookingsign selected for the datasets with and without the conditions, to easily compare them</li>
</ol>

```{r}
progressBar(id = "startpb", value = 0, display_pct = TRUE, size = 'lg')
```

## row 2 {data-width=350, .tapset}

### CSV with event data 
```{r}
fileInput("file1", "Dataset of the attack, separated by ;",
        accept = c(
          "text/csv",
          "text/comma-separated-values,text/plain",
          ".csv"))
```

### CSV with comparison data 
```{r}
fileInput("file2", "Dataset to compare, separated by ;",
        accept = c(
          "text/csv",
          "text/comma-separated-values,text/plain",
          ".csv"))
```


# DASHBOARD

## Column {.sidebar}


```{r}
selectInput(inputId = "bookingsign",
                  label = "Type of transaction:",
                  choices = NULL,
                  multiple = F
                  )
actionBttn("reload", "COMPUTE RULES", color = 'warning', style = 'simple')
progressBar(id = "reloadpb", value = 0, display_pct = TRUE)

selectInput(inputId = "mode",
                  label = "Choose pax attributes:",
                  choices = NULL,
                  multiple = T
                  )

actionBttn("update", "UPDATE", color = 'success', style = 'simple')

```

```{r}
observe({
req(input$file1, input$file2)
showModal(ui = (modalDialog("Loading datasets... can take up to 30s", footer=NULL)))

updateProgressBar(session = session, id = "startpb", value = 30)  
data_attack =  data_attack()
updateProgressBar(session = session, id = "startpb", value = 60)
data_compare = data_compare()
updateProgressBar(session = session, id = "startpb", value = 80)
updateProgressBar(session = session, id = "startpb", value = 100)
updateSelectInput(inputId = 'bookingsign', choices = unique(data_attack$bookingsign), selected = 'FULL_CANCELLATION')

removeModal()
})
```

```{r}

observeEvent(input$reload,{
  req(input$bookingsign)
  
data_attack =  data_attack()
data_compare = data_compare()
updateProgressBar(session = session, id = "reloadpb", value = 10)
rules_attack_df = data_attack[, c(6,8,10,11,12)]
updateProgressBar(session = session, id = "reloadpb", value = 15)
rules_compare_df = data_compare[, c(6,8,10,11,12)]
updateProgressBar(session = session, id = "reloadpb", value = 25)
rules_attack_df = as(rules_attack_df, "transactions")
updateProgressBar(session = session, id = "reloadpb", value = 35)
rules_compare_df = as(rules_compare_df, "transactions")
updateProgressBar(session = session, id = "reloadpb", value = 50)

rules_attack <- apriori (data=rules_attack_df, parameter=list (supp=0.001, conf = table(data_attack$bookingsign)[[input$bookingsign]]/sum(table(data_attack$bookingsign))), appearance = list(default="lhs",rhs=paste("bookingsign=", input$bookingsign, sep = '')), control = list (verbose=F))
updateProgressBar(session = session, id = "reloadpb", value = 70)
rules_compare <- apriori (data=rules_compare_df, parameter=list (supp=0.001, conf = table(data_attack$bookingsign)[[input$bookingsign]]/sum(table(data_attack$bookingsign))), appearance = list(default="lhs",rhs=paste("bookingsign=", input$bookingsign, sep = '')), control = list (verbose=F))
updateProgressBar(session = session, id = "reloadpb", value = 80)

datalist = list()
n = 0
for (i in colnames(rules_attack_df)){
  skip = F
  tryCatch(
    expr = {
      n = n + 1
      sub = DATAFRAME(subset(rules_attack, subset = lhs %in% i))
      sub2 = DATAFRAME(subset(rules_compare, subset = lhs %in% i))
      dat = data.frame(condition = i, value = sum(log(sub$support) * sub$confidence * sub$lift^2) / sum(log(sub2$support) * sub2$lift^2 * sub2$confidence), quantity_attack = max(sub$count), quantity_compare = max(sub2$count))
      datalist[[n]] = dat },
    error = function(e) {skip = T}
  )
  if(skip) {next}

}
updateProgressBar(session = session, id = "reloadpb", value = 90)
datasett$mainRules = do.call(rbind, datalist)

datasett$mainRules = datasett$mainRules[order(datasett$mainRules$value, decreasing = T),]
updateProgressBar(session = session, id = "reloadpb", value = 100)
# vtop = c()
# vmin = c()
# 
# for (s in c(1,2)) {
# vtop = c(vtop, str_split(top_n(mainRules, 2, value)$condition[s], "="))
# vmin = c(vmin,str_split(top_n(mainRules,- 2, value)$condition[s], "="))
# str_split(mainRules$condition[1], '=')
# }

updateSelectInput(inputId = "mode",choices = datasett$mainRules$condition, selected = datasett$mainRules$condition[1])
 
                  
})             
                
```



```{r}
observeEvent(input$update, {
  req(input$mode)
  
data_attack =  data_attack()
data_compare = data_compare()

fix1 = data_attack[, c(1,6,8,10,11,12)]
fix2 = data_compare[, c(1,6,8,10,11,12)]

g1 = fix1 %>% count(bookingsign, bookingdate)
g1 = g1[counts1$bookingsign == input$bookingsign,]
g1$values = g1$n/(fix1 %>% count(bookingdate))$n

g2 = fix2 %>% count(bookingsign, bookingdate)
g2 = g2[counts1$bookingsign == input$bookingsign,]
g2$values = g2$n/(fix1 %>% count(bookingdate))$n


RBPD2014 = read.csv("RelativeBookingsPerDay2014.csv", sep=';')
RBPD2015 = read.csv("RelativeBookingsPerDay2015.csv", sep=';')


for (i in 1:length(input$mode)) {
  var_condition = unlist(str_split(input$mode[i], '='))
  fix1 = fix1[fix1[[var_condition[1]]] == var_condition[2],]
  fix2 = fix2[fix2[[var_condition[1]]] == var_condition[2],]
}


counts1 = fix1 %>% count(bookingsign, bookingdate)
counts1 = counts1[counts1$bookingsign == input$bookingsign,]
counts1$partial = counts1$n/(fix1 %>% count(bookingdate))$n
 
counts2 = fix2 %>% count(bookingsign, bookingdate)
counts2 = counts2[counts2$bookingsign == input$bookingsign,]
counts2$partial = counts2$n/(fix2 %>% count(bookingdate))$n

datasett$forplot = data.frame(partial_attack = counts1$partial, partial_compare = counts2$partial, total_attack = g1$values, total_compare = g2$values)
datasett$forplot = melt(datasett$forplot, variable.name = 'year')

year_attack = unlist(str_split(data_attack$bookingdate[1], "-"))[1]
year_compare = unlist(str_split(data_compare$bookingdate[1], "-"))[1]
datasett$forplot$Year = c(rep(year_attack, 28), rep(year_compare, 28), rep(year_attack, 28), rep(year_compare, 28))

msg = "Only passengers with\n"
for (val in input$mode) {
  msg = paste(msg, paste(val, collapse = '=', sep=''), ' & ', sep ='')
}

datasett$forplot$Applied_to = c(rep(gsub('.{4}$', '', msg), 56),
                         rep('All passengers', 56))

})
```

## Column {.tabset .tabset-fade}

### Plot1

```{r}
renderPlot({
  req(datasett$mainRules)
  
  
  ggplot(datasett$mainRules, aes(x = reorder(datasett$mainRules$condition, -datasett$mainRules$value), y=datasett$mainRules$value, fill = datasett$mainRules$value > 1)) +
    geom_bar(stat="identity") + scale_fill_manual('Influential for event year', values = c("firebrick", "lightgreen")) +
    geom_hline(yintercept=1, linetype="dashed", color = "red") +     
    labs(title= paste("Most important attributes for a", input$bookingsign,"transaction on the event year"),
        y ="Score\n", x = "Attributes") +
    theme_bw() +
      theme(axis.text.x = element_text(angle = 90), plot.title = element_text(hjust = 0.5)) 
  
  
})
```

The higher the score, the more impactful that attribute of the passenger is for a ```{r}input$bookingsign``` transaction. For full cancellations for example, attributes losname=STAY and paxprofile=BUSINESS have high scores, that means people with those attributes were more likely to cancel during the time of the attack, specially in comparison with a normal month. Knowing this information beforehand would enable us to get ready for "crystal" passengers, in case of a major disaster. 

On the other hand, the red bars mean that people with those characteristics were less likely to cancel during the attack (specially in comparison with a normal month). This information is crucial as it lets us know which kind of passengers would travel notwithstanding any problem in the destination. 

You can choose a combination of attributes in the left side of the DASHBOARD page, click the button, and the plot will update. Notice how big the difference is between the month of the event with the conditions and the other lines. Notice also how there is no big difference between the normal month and the normal month with the conditions, this is because the conditions of the passengers are specially important for a cancellation due to the event/attack, not for any other reason.

### Plot2

 

```{r}

renderPlot({
  req(datasett$forplot) 
  
  ggplot(datasett$forplot, aes(x = rep(1:28,4), y=datasett$forplot$value)) +
  geom_line(aes(color = datasett$forplot$Year, linetype = datasett$forplot$Applied_to), size = 1.2) +

  labs(title= paste(input$bookingsign,"throughout the month"),
        y =paste("% of transactions that are" ,input$bookingsign,"\n"), x = "Days") +
  theme_bw() +

  theme(plot.title = element_text(hjust = 0.5))
})
```



