---
title: "R Notebook"
output: html_notebook
---

Data preparation: 

```{r warning=FALSE}
library(arules)
nov2015 = read.csv(file = 'Nov2015.csv', sep = ';')
nov2014 = read.csv(file = 'Nov2014.csv', sep = ';')

reglas_2015 = nov2015[, c(6,8,10,11,12)]
reglas_2014 = nov2014[, c(6,8,10,11,12)]
reglas_2015 = as(reglas_2015, "transactions")
reglas_2014 = as(reglas_2014, "transactions")
```

Apriori algorithm to find rules that most influence a decision of FULL CANCELLATION of the trip. Support = .1% and confidence = 8%, which is the minimun requirement because that's approximately the amount of FULL CANCELLATIONS of the dataset, a lower number is not interesting for our study, lift also has to be > 1  

```{r}
rules_2015_Cancel <- apriori (data=reglas_2015, parameter=list (supp=0.001, conf = 0.08), appearance = list(default="lhs",rhs="bookingsign=FULL_CANCELLATION"), control = list (verbose=F))
rules_2014_Cancel <- apriori (data=reglas_2014, parameter=list (supp=0.001, conf = 0.08), appearance = list(default="lhs",rhs="bookingsign=FULL_CANCELLATION"), control = list (verbose=F))


rules_2015_Cancel_sort <- sort(rules_2015_Cancel, by="lift", decreasing=TRUE) 
rules_2014_Cancel_sort <- sort(rules_2014_Cancel, by="lift", decreasing=TRUE) 


head(DATAFRAME(rules_2015_Cancel_sort))[c(1,2,4,6,7)] #Only interesting columns
head(DATAFRAME(rules_2014_Cancel_sort))[c(1,2,4,6,7)]
```

We are doing the opposite now, trying to find the rules which conditions lead to a decision contrary to a FULL CANCELLATION. We get this by creating rules with confidence < 8%, (support stays the same as we want rather relevant rules) and then sorting by increasing lift. Its essentially the same study, but by sorting in a increasing way, we will find lift < 1 which is what we need in this case:


```{r}
rules_2015_NCancel <- apriori (data=reglas_2015, parameter=list (supp=0.001, conf = 0.008), appearance = list(default="lhs",rhs="bookingsign=FULL_CANCELLATION"), control = list (verbose=F))
rules_2014_NCancel <- apriori (data=reglas_2014, parameter=list (supp=0.001, conf = 0.008), appearance = list(default="lhs",rhs="bookingsign=FULL_CANCELLATION"), control = list (verbose=F))


rules_2015_NCancel_sort <- sort(rules_2015_NCancel, by="lift", decreasing=F) 
rules_2014_NCancel_sort <- sort(rules_2014_NCancel, by="lift", decreasing=F) 


head(DATAFRAME(rules_2015_NCancel_sort))[c(1,2,4,6,7)] #Only interesting columns
head(DATAFRAME(rules_2014_NCancel_sort))[c(1,2,4,6,7)]


```

We are working towards the creation/implementation of a metric that would allow us to compare both sets of rules (2014 and 2015) in a way that we could determine which conditions are more important in which ruleset. 

We have done this humanly by looking at the data. But it would be perfect if there was a way to numerically compare both sets. This is possible because both sets were created over the same conditions and with the same hyperparameters (both for the cancellations and the not cancellations)


```{r}
for (i in colnames(rules_2015_Cancel)){
  skip = F
  tryCatch(
    expr = {
      sub = DATAFRAME(subset(rules_2015_NCancel, subset = lhs %in% i))
      sub2 = DATAFRAME(subset(rules_2014_NCancel, subset = lhs %in% i))
      cat(sum(sub$support * sub$lift^2 * sub$confidence) / sum(sub2$support * sub2$lift^2 * sub2$confidence), "columna: ", i)
      cat('\n')},
    error = function(e) {skip = T}
  )
  if(skip) {next}

}
```

```{r}
for (i in colnames(rules_2015_Cancel)){
  skip = F
  tryCatch(
    expr = {
      sub = DATAFRAME(subset(rules_2015_Cancel, subset = lhs %in% i))
      sub2 = DATAFRAME(subset(rules_2014_Cancel, subset = lhs %in% i))
      cat(sum(sub$support * 1/sub$confidence * 1/sub$lift^2) / sum(sub2$support * 1/sub2$lift^2 * 1/sub2$confidence), "columna: ", i, max(sub$count))
      cat('\n')},
    error = function(e) {skip = T}
  )
  if(skip) {next}

}
```

